The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems

### 2012-04-23 shortRange.inhomo/alltext/pubilsh/main.tex
fix typos

\recheck{ One possible way to avoid the cut-off difficulty is to
  modify the short-range interaction by a shifting approach: inside a
  certain radius the origianl interaction is kept, while outside it the
  interaction is screen by a shift function, so that goes to
  zero smoothly. The amount of Shifting is minor in most cases,
  however, it actually changes the way of
  modelling molecules. For example, it
  has been shown that shifting the dispersion remarkably changes the
  phase diagram of the Lennard-Jones system~\cite{smit1992phase}.
  Since the dispersion term 
  can be derived by quantum mechanical arguments, and has the physical
  reality, the unshifted interaction is
  prefered and investigated by most studies
  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical, wang2010optimizing}).
  % Shifting the direct part of the Ewald summation actually
  % violates the Coulomb's law in the way that depends on the
  % splitting parameter, so it should be treated carefully.
  % Here we would like to suggest treating the shifting approach
  % as a special case 
}
% In this paper, we focus on the systems in which
% atoms/particles are interacting via short-range interactions, because
% it is a good starting point of the study of more complex systems, for
% example, the systems with long-range electrostatic interactions.  The
% simulation results in the inhomogeneous systems are found to depend on
% a number of factors of treating the short-range interaction in the
% simulation. For example, the way of calculating the short-range
% interaction (simple cut-off method or Ewald
% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
%   lopez2006liquid, shi2006molecular, ismail2007application}, the
% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
%   shen2007comparative}, the way of long-range
% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
%   goujon2004monte} and the size and shape of the simulation
% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
% It should be noticed that the physical properties are the nature of
% the system, and should NOT depend on the details of the interaction
% calculation.

@@

To show the
effectiveness of the error estimate and the proposed methods, two
systems are tested: the liquid-vapor equilibrium for equilibrium
properties, and the colliding nanoscale clusters for dynamical
properties.
\recheck{
  In these example, we investigate the Lennard-Jones interaction, which
  is one of the most widely used in molecular simulations.
  However, the error estimate,
  the adaptive cut-off and long-range correction methods
  are not restricted to the Lennard-Jones: it can
  be applied to other types of short-range interactions without 
  difficulty, such as
  Buckingham, the direct part of Ewald summation~\cite{ewald1921die}, etc..
  We want to stress that the main contribution and the research interest is the
  quantitative study of the force computation error by cuting-off
  the short-range interaction.
  The examples, which are comparatively simple and ideal,
  are used only for testing the validity of the error
  estimate and the proposed methods,
  and demostrating the role of different errors in the simulations.
  The error study in more realistic systems requires the
  estimates of the electrostatic interaction,
  which are calculated by the long-range algorithms, such as
  PME~\cite{darden1993pme}, SPME~\cite{essmann1995spm},
  P3M~\cite{deserno1998mue1}, etc..
  The space of the present paper is not enough for
  these algorithms, so they will be delivered in the future work.
}
% Finally, conclusions are given in section
% \ref{sec:conclusion}.

@@

The direct simulation of the liquid-vapor equilibrium is a very
typical inhomogeneous system, which is widely used to study the phase
coexistence properties, for example, the equilibrium liquid/vapor
density, and the surface tension. The system studied in the present
paper contains 16,000 identical standard Lennard-Jones particles that are
separated into liquid phase in the center of the periodic box and vapor phase
surrounded (see Fig.~\ref{fig:tmp1}).  The conventional Lennard-Jones
unit system is employed: the unit of length, energy, mass and time are
denoted by $\epsilon$, $\sigma$, $m$ and $\tau$ ($\tau =
\sigma\sqrt{m/\varepsilon}$), respectively.  In the rest of this paper,
all quantities are
rescaled by the Lennard-Jones units and added the superscript ``$\ast$''.
For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$,
$P^\ast = P\cdot \sigma^3 / \epsilon$ and $\mathcal E^\ast = \mathcal
E\cdot\sigma/\varepsilon$.  The MD time step {is} $\Delta t^\ast =
0.005$. The simulations last for $3\times 10^6$ time steps. The first
$1\times 10^6$ steps are discarded. The quantities of interest are
sampled every 100 time steps. The blocking average
method~\cite{flyvbjerg1989error} is applied to estimate the
statistical uncertainty of the autocorrelated data with 95\%
confidence level. The NVT ensemble is generated by the Nos\`e-Hoover
thermostat~\cite{nose1984molecular, hoover1985canonical}.  The size of
the simulation box is $L_x^\ast \times L_y^\ast \times L_z^\ast =
150\times 21\times 21$, which permits a maximum cut-off radius of
$r_c^\ast = 10$, and eliminates the finite size effect reported in
literatures \cite{chen1995area, orea2005oscillatory,
  biscay2009calculation}.
The system is divided into bins of size $1\times1\times1$ to perform the fast error
estimate method described in section \ref{sec:tmp1.3}.
In all simulations, the maximum cut-off
radius considered is $10$, but the reference results for comparison
are obtained by simulations carried out in a 24,000 particles system
with simulation box $L_x^\ast \times L_y^\ast \times L_z^\ast =
150\times 27\times 27$, and a uniform cut-off radius of $r_c^\ast =
13$.  {We find that (not shown here)
  the bigger system leads to the same equilibrium
  quantities as the smaller system at the same cut-off radius, so
  it is reasonable to
  use it to produce the better converged data at $r_c^\ast=13$ and compare them with
  those obtained in the smaller system.
}

@@

\recheck{
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate can be more general than the studied examples.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald summation, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spirical interfaces)
  can be easily studied by the error estiamtes and the proposed methods.
  The error study of
  more realistic systems requires the error estiamtes of the long-range
  algoritms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}

>>>>

\recheck{ One possible way to avoid the cut-off difficulty is to
  modify the short-range interaction by a shifting approach: inside a
  certain radius the original interaction is kept, while outside it the
  interaction is screen by a shift function, so that goes to
  zero smoothly. The amount of Shifting is minor in most cases,
  however, it actually changes the way of
  modeling molecules. For example, it
  has been shown that shifting the dispersion remarkably changes the
  phase diagram of the Lennard-Jones system~\cite{smit1992phase}.
  Since the dispersion term 
  can be derived by quantum mechanical arguments, and has the physical
  reality, the unshifted interaction is
  preferred and investigated by most studies
  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical, wang2010optimizing}).
  % Shifting the direct part of the Ewald summation actually
  % violates the Coulomb's law in the way that depends on the
  % splitting parameter, so it should be treated carefully.
  % Here we would like to suggest treating the shifting approach
  % as a special case 
}
% In this paper, we focus on the systems in which
% atoms/particles are interacting via short-range interactions, because
% it is a good starting point of the study of more complex systems, for
% example, the systems with long-range electrostatic interactions.  The
% simulation results in the inhomogeneous systems are found to depend on
% a number of factors of treating the short-range interaction in the
% simulation. For example, the way of calculating the short-range
% interaction (simple cut-off method or Ewald
% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
%   lopez2006liquid, shi2006molecular, ismail2007application}, the
% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
%   shen2007comparative}, the way of long-range
% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
%   goujon2004monte} and the size and shape of the simulation
% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
% It should be noticed that the physical properties are the nature of
% the system, and should NOT depend on the details of the interaction
% calculation.

@@

To show the
effectiveness of the error estimate and the proposed methods, two
systems are tested: the liquid-vapor equilibrium for equilibrium
properties, and the colliding nanoscale clusters for dynamical
properties.
\recheck{
  In these example, we investigate the Lennard-Jones interaction, which
  is one of the most widely used in molecular simulations.
  However, the error estimate,
  the adaptive cut-off and long-range correction methods
  are not restricted to the Lennard-Jones: it can
  be applied to other types of short-range interactions without 
  difficulty, such as
  Buckingham, the direct part of Ewald summation~\cite{ewald1921die}, etc..
  We want to stress that the main contribution and the research interest is the
  quantitative study of the force computation error by cutting-off
  the short-range interaction.
  The examples, which are comparatively simple and ideal,
  are used only for testing the validity of the error
  estimate and the proposed methods,
  and demonstrating the role of different errors in the simulations.
  The error study in more realistic systems requires the
  estimates of the electrostatic interaction,
  which are calculated by the long-range algorithms, such as
  PME~\cite{darden1993pme}, SPME~\cite{essmann1995spm},
  P3M~\cite{deserno1998mue1}, etc..
  The space of the present paper is not enough for
  these algorithms, so they will be delivered in the future work.
}
% Finally, conclusions are given in section
% \ref{sec:conclusion}.

@@

The direct simulation of the liquid-vapor equilibrium is a very
typical inhomogeneous system, which is widely used to study the phase
coexistence properties, for example, the equilibrium liquid/vapor
density, and the surface tension. The system studied in the present
paper contains 16,000 identical standard Lennard-Jones particles that are
separated into liquid phase in the center of the periodic box and vapor phase
surrounded (see Fig.~\ref{fig:tmp1}).  The conventional Lennard-Jones
unit system is employed: the unit of length, energy, mass and time are
denoted by $\epsilon$, $\sigma$, $m$ and $\tau$ ($\tau =
\sigma\sqrt{m/\varepsilon}$), respectively.  In the rest of this paper,
all quantities are
rescaled by the Lennard-Jones units and added the superscript ``$\ast$''.
For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$,
$P^\ast = P\cdot \sigma^3 / \epsilon$ and $\mathcal E^\ast = \mathcal
E\cdot\sigma/\varepsilon$.  The MD time step {is} $\Delta t^\ast =
0.005$. The simulations last for $3\times 10^6$ time steps. The first
$1\times 10^6$ steps are discarded. The quantities of interest are
sampled every 100 time steps. The blocking average
method~\cite{flyvbjerg1989error} is applied to estimate the
statistical uncertainty of the autocorrelated data with 95\%
confidence level. The NVT ensemble is generated by the Nos\`e-Hoover
thermostat~\cite{nose1984molecular, hoover1985canonical}.  The size of
the simulation box is $L_x^\ast \times L_y^\ast \times L_z^\ast =
150\times 21\times 21$, which permits a maximum cut-off radius of
$r_c^\ast = 10$, and eliminates the finite size effect reported in
literature~\cite{chen1995area, orea2005oscillatory,
  biscay2009calculation}.
The system is divided into bins of size $1\times1\times1$ to perform the fast error
estimate method described in section \ref{sec:tmp1.3}.
In all simulations, the maximum cut-off
radius considered is $10$, but the reference results for comparison
are obtained by simulations carried out in a 24,000 particles system
with simulation box $L_x^\ast \times L_y^\ast \times L_z^\ast =
150\times 27\times 27$, and a uniform cut-off radius of $r_c^\ast =
13$.  {We find that (not shown here)
  the bigger system leads to the same equilibrium
  quantities as the smaller system at the same cut-off radius, so
  it is reasonable to
  use it to produce the better converged data at $r_c^\ast=13$ and compare them with
  those obtained in the smaller system.
}

@@

\recheck{
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate can be more general than the studied examples.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald summation, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spherical interfaces)
  can be easily studied by the error estimates and the proposed methods.
  The error study of
  more realistic systems requires the error estimates of the long-range
  algorithms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}
